Intentional release of native species undermines ecological stability

### 2022-12-23 rmd/manuscript.Rmd
edit: add text for additional predictors

In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$. The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas. Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **Model fitting**). Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use. Urban and agricultural land use was omitted because of either a limited value range (**Figure S**14) or a strong correlation with forest land use (**Figure S**15). The watershed-specific intercept was related to a watershed-level predictor as:

$$
\begin{aligned}\begin{split}\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\\theta_{\gamma,w} &= \gamma'_0 + \gamma'_1 x'_{w}\end{split}\end{aligned}
$${#eq:random-eff}

$\gamma'_{0}$ is the global intercept and $\gamma'_1$ is the regression coefficient of ocean productivity $\gamma'_{w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019). Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictor cannot capture.

>>>>

In Equation \@ref(eq:effr), $\eta_{w,s'}$ represents the effective proportion of total release affecting the community at site $s'$ within watershed $w$. The summation of $\eta_{w,s'}$ over $S_w+1$ is assumed to be unity because a non-negligible portion of release may escape into unsurveyed areas. Since the values of $\eta_{w,s'}$ are not available in our dataset, we estimated them through a stochastic search while fitting the regression model to the data within a Bayesian framework (see **Model fitting**). Other site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, forest land use, and the number of observation years. The number of observation years was included as a control factor given the potential influence on the estimates of temporal community variability. Urban and agricultural land use was omitted because of either a limited value range (**Figure S**14) or a strong correlation with forest land use (**Figure S**15). The watershed-specific intercept was related to a watershed-level predictor as:

$$
\begin{aligned}\begin{split}\gamma_{0,w} &\sim \text{Normal}(\theta_{\gamma,w},\sigma_{\gamma}^2)\\\theta_{\gamma,w} &= \gamma'_0 + \sum_k \gamma'_k x'_{k,w}\end{split}\end{aligned}
$${#eq:random-eff}

$\gamma'_{0}$ is the global intercept and $\gamma'_k$ is the regression coefficients of ocean productivity $\gamma'_{1,w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019) and standard deviation of elevation (SD elevation) within an entire watershed $\gamma'_{2,w}$. Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous). SD elevation is a landscape-level variable that may dictate long-term flow dynamics. The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.
